---
title: "ASA_Assignment_1"
author: "Shreyas Namjoshi"
date: "23/03/2022"
output: html_document
---

```{r setup, include=FALSE}
setwd("E:\\ISB\\Term4\\ASA\\Assignment")
library("MASS")
library("ISLR")
library("readxl")
library("klaR")
library(caret)

```

## R Markdown

    Loading the data and dividing it in Train and Test

```{r}
data<-read_excel("FinalDataSet_ASA.xlsx")
## 70% of the data for training
train_size <- floor(0.70 * nrow(data))

## set the seed to make your partition reproducible
set.seed(213)
train_ind <- sample(seq_len(nrow(data)), 
                    size = train_size)
train <- data[train_ind,]
test <- data[-train_ind,]
```
  
<span style="color: blue;">Q1.  Build a Discriminant Analysis Model to predict whether the person is likely to 
accept the bank’s offer for a personal loan. If necessary, create new variables to 
improve the model performance.</span>

```{r}
lda.fit<-lda(data$`Personal Loan`~.,data=data,subset = train_ind)
lda.fit

plot(lda.fit, type='b')


```
    
      Here from the plot we can see that there is clear difference between 2 classes (availed and not availed) with very less overlap or misclassification between the two classes.
      
      
      
<span style="color: blue;">Q2.  Carry out significance tests using Wilk’s Lambda.</span>
      

      Assuming alpha=0.1
      
```{r}
dependent1=train$`Personal Loan`
formulaAll= dependent1 ~ train$Age+train$Experience+train$Income+train$`ZIP Code`+train$Family+train$CCAvg+train$Education+train$Mortgage+train$`Securities Account`+train$`CD Account`+train$Online+train$CreditCard
print(formulaAll)
greedy.wilks(formulaAll,data=train,niveau = 0.1) 

```
     
<span style="color: blue;">Q3.  Comment on the variables that are significant</span>
     
     Comment:From the above table, the variables that are significant with cut off= 0.1 are Income,CD Account,Education,Family,CCAvg and Credit Card.SO even if we drop rest of the variables from our model, our prediction is not going to change much.

     
<span style="color: blue;">4.  Create the confusion matrix and comment on the prediction accuracy.</span>
     
     Here we get the prediction accuracy for test set(300 Records)
```{r}
lda.pred <- predict(lda.fit, test)
results <- confusionMatrix(data=lda.pred$class, reference=as.factor(test$`Personal Loan`))
print(results)
```
      
      From the above output, it is seen that Prediction Accuracy is 92% with sensitivity as 98% and specificity as 44%.
      
<span style="color: blue;">5. The bank would like to address the top 30 persons with an offer for personal loan 
based on the probability (propensity). Create a table displaying all the details of the 
“top” 30 persons who are most likely to accept the bank’s offer. Make sure to 
include the probability of accepting the offer along with all the other details.</span>
      
      
      Here we are including only test set to find the top 30 person who are most likely to accept bank offer based on probability
```{r}
probdf<-lda.pred$posterior
test['Prob of Availing']<-probdf[,"1"]
test<-test[order(test$`Prob of Availing`,decreasing = TRUE),]
head(test,n=30)
```
      


     
     