---
title: "ASA_Assignment_2"
author: "Shreyas Namjoshi"
date: "23/03/2022"
output: html_document
---
```{r setup, include=FALSE}
setwd("E:\\ISB\\Term4\\ASA\\Assignment")
library("MASS")
library("ISLR")
library("readxl")
library("klaR")
library(caret)

```

## R Markdown

    Loading the data and dividing it in Train and Test

```{r}
data<-read_excel("FinalDataSet_ASA.xlsx")
## 70% of the data for training
train_size <- floor(0.70 * nrow(data))

## set the seed to make your partition reproducible
set.seed(213)
train_ind <- sample(seq_len(nrow(data)), 
                    size = train_size)
train <- data[train_ind,]
test <- data[-train_ind,]
```


<span style="color: blue;">Q1. Build a logistic regression equation to predict whether the person is likely to accept 
the bank’s offer for a personal loan. If necessary, create new variables to improve 
the model performance.</span>
```{r}
Default.Model <- glm(train$`Personal Loan` ~ ., data=train, family = binomial)
summary(Default.Model)
```
      
<span style="color: blue;">Q2. Carry out the omnibus test to test whether the model as a whole is significant. 
Comment on the result of the omnibus test.</span>

```{r}
library(lmtest)
lrtest(Default.Model)
```

      Here We reject the Model 2 as we have sufficient evidence that model 2(model with only intercept) is not good (assumed value of alpha is 0.05).This means that atleast one of the coeff is significant.
      
      
<span style="color: blue;">Q3.Test the hypothesis that βj = 0 for all βj, where βj indicates the coefficient 
corresponding to jth explanatory variable. Comment on the result of these
hypothesis tests.</span>
```{r}
summary(Default.Model)
```
      
      Comment: In the above table, P value represents the Walds Test P Value. Thus only significant variables contributing to the model are Income,Family,CCAvg,Education,CD Account, Credit Card. Rest of the coefficients are non significant.
      
<span style="color: blue;">Q4.Carry out the hypothesis test that the model fits the data. Comment on the results.</span>
```{r}
library(ResourceSelection)
hoslem.test(Default.Model$y, fitted(Default.Model))

```

      From the above P value, we do not have sufficient evidence to reject Null hypothesis. This implies that model fits the data well.
      
      
<span style="color: blue;">Q5.The bank would like to address the top 30 persons with an offer for personal loan 
based on the probability (propensity). Create a table displaying all the details of the
“top” 30 persons who are most likely to accept the bank’s offer. Make sure to 
include the probability of accepting the offer along with all the other details.</span>
      
      
       Here we are including only test set to find the top 30 person who are most likely to accept bank offer based on probability
       
```{r}
pred<-as.data.frame(predict(Default.Model,test[,-9],type = "response"))
pred

test['Prob of Availing']<-pred
test1<-test[order(test$`Prob of Availing`,decreasing = TRUE),]
testLG<-head(test1,n=30)
testLG

```
      
<span style="color: blue;">Q6. Compare the above list of 30 persons against the 30 persons obtained from 
Discriminant Analysis (Assignment 1). Comment on the similarities and 
dissimilarities</span>

      
```{r}

lda.fit<-lda(data$`Personal Loan`~.,data=data,subset = train_ind)
#lda.fit
lda.pred <- predict(lda.fit, test)
probdf<-lda.pred$posterior
test['Prob of Availing LDA']<-probdf[,"1"]
test['class']<-lda.pred$class
testLDA<-test[order(test$`Prob of Availing LDA`,decreasing = TRUE),]
testLDA30<-head(testLDA,n=30)
summary(testLDA30)

```


```{r}
summary(testLG)
```
```{r}
print("Education Count")

table(testLG$Education)
table(testLDA30$Education)

print("CD Count")

table(testLG$`CD Account`)
table(testLDA30$`CD Account`)

print("Credit Card Count")

table(testLG$CreditCard)
table(testLDA30$CreditCard)

print("CM for LDA for test set")
resultsLDA <- confusionMatrix(data=testLDA30$class, reference=as.factor(testLDA30$`Personal Loan`))
print(resultsLDA)

print("CM for LR for test set")
predicted<-as.numeric(testLG$`Prob of Availing`>0.5)
resultsLG<-confusionMatrix(data = as.factor(predicted), reference = as.factor(testLG$`Personal Loan`))
print(resultsLG)


```

        1. we see similarities in both the output's with respect to age,income,family, and CCAvg,securities Account
        2. We can see that there are more people with education as UG and Graduate in LDA than in Logistic.
        3. We see that in LDA, more number of people are there who have Certificate of Deposit
        4. We also see that number of people who use credit are more in LDA than in Logistic Regression
        5. We also see improved level of accuracy,specificity and sensitivity for Logistic Regression as compared to LDA for test data.
        
      